COVID-19 and Online Learning Tools

### 2021-12-28 Paper_online_Learning.tex
update intro

Even though distance education has a long history that goes back almost two centuries with significant modifications,
alterations, and additions in the process of delivery and communication \autocite{moore2011learning,spector2014handbook}, COVID-19 certainly created a new era of distance education while encouraging various stakeholders in education to take the concept of distance education seriously \autocite{richmond2020critical}. Sudden unexpected movement from classrooms to home schooling at large-scale made students, teachers and parents vulnerable, leading to millions of education related internet searches being performed during the period of COVID-19 pandemic (Figures \ref{fig:distanceLearningWorldAnalysis}) \autocite{carter2021teacher}. Surprisingly, the search spikes of distance education related searches (Figure \ref{fig:distanceLearningWorldAnalysis} (c)) coincide with increasing COVID-19 counts (Figure \ref{fig:distanceLearningWorldAnalysis} (a)) and related internet searches (Figure \ref{fig:distanceLearningWorldAnalysis} (b)), even though distance education has a long history in contrast to the COVID-19 pandemic.

>>>>

Even though distance education has a long history that goes back almost two centuries with significant modifications,
alterations, and additions in the process of delivery and communication \autocite{moore2011learning,spector2014handbook,zawacki2016mapping}, COVID-19 certainly created a new era of distance education while encouraging various stakeholders in education to take the concept of distance education seriously \autocite{richmond2020critical}. Sudden unexpected movement from classrooms to home schooling at large-scale made students, teachers and parents vulnerable, leading to millions of education related internet searches being performed during the period of COVID-19 pandemic (Figures \ref{fig:distanceLearningWorldAnalysis}) \autocite{carter2021teacher}. Surprisingly, the search spikes of distance education related searches (Figure \ref{fig:distanceLearningWorldAnalysis} (c)) coincide with increasing COVID-19 counts (Figure \ref{fig:distanceLearningWorldAnalysis} (a)) and related internet searches (Figure \ref{fig:distanceLearningWorldAnalysis} (b)), even though distance education has a long history in contrast to the COVID-19 pandemic.

### 2021-12-28 main.Rmd
update intro

Even though distance education has a long history that goes back  almost two centuries with significant  modifications,
alterations, and additions in the process of delivery and communication  [@moore2011learning; @spector2014handbook],  COVID-19 certainly created a new era of distance education while encouraging various stakeholders in education to take the concept of distance education seriously [@richmond2020critical].  Sudden unexpected movement from classrooms to home schooling at large-scale made  students, teachers and parents vulnerable, leading to millions of education related internet searches being performed during the period of COVID-19 pandemic (Figures \ref{fig:distanceLearningWorldAnalysis}) [@carter2021teacher]. Surprisingly, the search spikes of distance education related searches (Figure \ref{fig:distanceLearningWorldAnalysis} (c)) coincide with increasing COVID-19 counts (Figure \ref{fig:distanceLearningWorldAnalysis} (a)) and related internet searches (Figure \ref{fig:distanceLearningWorldAnalysis} (b)), even though distance education has a long history in contrast to the COVID-19 pandemic.

>>>>

Even though distance education has a long history that goes back  almost two centuries with significant  modifications,
alterations, and additions in the process of delivery and communication  [@moore2011learning; @spector2014handbook; @zawacki2016mapping],  COVID-19 certainly created a new era of distance education while encouraging various stakeholders in education to take the concept of distance education seriously [@richmond2020critical].  Sudden unexpected movement from classrooms to home schooling at large-scale made  students, teachers and parents vulnerable, leading to millions of education related internet searches being performed during the period of COVID-19 pandemic (Figures \ref{fig:distanceLearningWorldAnalysis}) [@carter2021teacher]. Surprisingly, the search spikes of distance education related searches (Figure \ref{fig:distanceLearningWorldAnalysis} (c)) coincide with increasing COVID-19 counts (Figure \ref{fig:distanceLearningWorldAnalysis} (a)) and related internet searches (Figure \ref{fig:distanceLearningWorldAnalysis} (b)), even though distance education has a long history in contrast to the COVID-19 pandemic.
